A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-02-17 src/tex/ms.tex

The distance a stellar population born at $R_{\rm form}$ migrates over its age $\tau$ is drawn from a Gaussian centered at 0 with standard deviation
\begin{equation}
    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61},
    \label{eq:radial-migration}
\end{equation}
where we adopt $\sigma_{\rm RM8}=2.68$ kpc as the fiducial value for the strength of radial migration. This is smaller than the value of $\sigma_{\rm RM8}=3.6$ kpc found by \citet{frankel_measuring_2018}, but in \todo{Section X} we explore the effect of a stronger migration prescription.

@@

>>>>

The distance a stellar population born at $R_{\rm form}$ migrates over its age $\tau$ is drawn from a Gaussian centered at 0 with standard deviation
\begin{equation}
    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61},
    \label{eq:radial-migration}
\end{equation}
where we adopt $\sigma_{\rm RM8}=2.68$ kpc as the fiducial value for the strength of radial migration. This is smaller than the value of $\sigma_{\rm RM8}=3.6$ kpc found by \citet{frankel_measuring_2018}, but in Section \ref{sec:age-abundance} we explore the effect of a stronger migration prescription.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/mdf_evolution.pdf}
    \caption{Caption.}
    \label{fig:mdf-evolution}
\end{figure*}
